A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.

### 2015-02-23 paper/draft.tex
LF model
Intro, Obs. data, SFR
Willott observations paragraph added, also SFR vs. DM (w/wo dust)figures
Refs. in observations. Removing intro. Methodology main ideas.

\documentclass[manuscript]{aastex}
%\documentclass[preprint2]{aastex}
%\usepackage{graphicx}
%\usepackage{graphics}
%\usepackage[dvips]{epsfig}
\usepackage{epstopdf}

@@

\begin{abstract}
This work relates baryonic matter and dark matter at redshift $z=5.9$ using 
observational data from CFHTLS \citep{willott13}, HUDF09 
\citep{bouwens06,bouwens12}, UKIDSS and SDXS \citep{mclure09}, and results of 
the Multidark Simulation \citep{riebe13} in a cubic box of $1000 \textrm{Mpc 
h}^{-1}$ length with 2013 Planck Cosmology. The Luminosity Function (LF) is 
fitted via four parameters with the Markov Chain Monte Carlo method. The 
relationship between the Dark Matter Halos Mass and Star Formation Rate is 
obtained using the relationship between the UV  continuum (from the fitted LF) 
and Star Formation Rate (SFR) by \cite{kennicutt98}.Cosmic variance effects are 
studied on smaller boxes of $250 \textrm{Mpc h}^{-1}$ length.

@@

\include{introduction}

@@

@@

\section{Appendix material}
DEXTER \url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}

>>>>

\documentclass[manuscript]{aastex}
%\documentclass[preprint2]{aastex}
%\usepackage{graphicx}
%\usepackage{graphics}
%\usepackage[dvips]{epsfig}
\usepackage{epstopdf}
\usepackage{color}

@@

\begin{abstract}
This work relates baryonic matter and dark matter at redshift $z=5.9$ using 
observational data from CFHTLS \citep{willott13}, HST Legacy Survey
\citep{bouwens14,finkelstein14}, UKIDSS and SDXS \citep{mclure09}, and results of 
the Multidark Simulation \citep{riebe13} in a cubic box of $1000 \textrm{Mpc 
h}^{-1}$ length with 2013 Planck Cosmology. The Luminosity Function (LF) is 
fitted via four parameters with the Markov Chain Monte Carlo method. The 
relationship between the Dark Matter Halos Mass and Star Formation Rate is 
obtained using the relationship between the UV  continuum (from the fitted LF) 
and Star Formation Rate (SFR) by \cite{kennicutt98}.Cosmic variance effects are 
studied on smaller boxes of $250 \textrm{Mpc h}^{-1}$ length.

@@

%\include{introduction}

@@

\include{methodology}

@@

%\section{Appendix material}
%DEXTER \url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}

### 2015-02-23 paper/observations.tex
Refs. in observations. Removing intro. Methodology main ideas.

The data from the Hubble Space Telescope Legacy (HSTL) \citep{bouwens14} is a compilation 
of observations since the installation of the Advanced Camera for Surveys (ACS) in 2002, 
through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in 2009, up to 2012. 
The HST fields of view are: XDF, HUDF09-1, HUDF09-2, CANDELS-S/Deep, 
CANDELS-S/Wide, ERS, CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS, 
CANDELS-COSMOS and CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2, 
40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area corresponds 
to $\sim 0.7 \deg^2$ over five different lines of sight, reducing cosmic variance effects. 
Two cameras performed the observations: ACS and WFC3/IR, using 
$B_{435} V_{606} i_{814} z_{850} I_{814} Y_{098} Y_{105} J{125} JH_{140}$ and $H_{160}$ filters.
The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in the 
deepest field (XDF). Total number of z=6 LBG candidates is 940, most of them in the faint 
end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
The Schechter parameters derived are: $\phi^* / \textrm{Mpc}^{-3} =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}$, $M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. \citet{bouwens14} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.

\citet{willott13} presented the sixth release of the Canada-France-Hawaii 
Telescope Legacy Survey CFHTLS. The observations where performed over four 
separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives this 
survey great robustness. Optical observations used MegaCam 
[CITE REQUIRED] with $u^* g' r' i' z'$ filters. The main selection criteria: all the 
objects must be brighter than magnitude $z' = 25.3$. The final 
number of LBGs founded was 40. Moreover, they get spectroscopic confirmation 
for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which 
has a $\ll 5.5$-square arcmin field of view . They show incompleteness in the sample due to 
foreground contamination and the detection algorithm; there is no warranty to 
have every object brighter than the limit magnitude on the faint limit. The full 
galaxy LF at $z=6$ cannot be obtained as in other studies. Nevertheless, this survey 
was focussed on the highly luminous LBGs. LF is calculated using the stepwise 
maximum likelihood method of Efstathiu et al. [MNRAS 1998 Cite required!!!], within 
magnitudes 
from $M_{1350} = -22.5$ up to $-20.5$. The luminosity function of $z=5.9$ shows 
an exponential decline at the bright end, where feedback processes and inefficient 
last cooling limites star forming in bright galaxies hosted in the most massive halos.

\citet{mclure09} build the luminosity function for $z=5$ and $z=6$ using data from two ground-based
 telescopes: the United Kingdom Infrared Telescope in the near-IR imaging and Subaru 
 Telescope for the optical imaging. They use the first data release of the UKIRT Infrared 
 DeepSky Survey Ultra Deep Survey (UDS), together with the Subaru XMM-Newton 
 Survey (SXDS). Total observed area is $0.63 \deg^2$ uniformly covered by booth catalogues.
The UKIRT was equipped with the WFCAM using $J K$ filters. The Subaru was equipped 
with the Suprime-Cam with the $B V R i' z'$ filters. All candidates where brighter than 
$z'=26$. The UV rest frame magnitude range is $-22.4\leq M_{1500} \leq-20.6$. The LF 
was calculated using the maximum likelihood estimator of Schmidt (1968). [Cite Required!!!!]. 
Their analysis gave a total number of 104 LBG candidates in the redshift range 
$5.7\leq z \leq 6.3$. LF was parameterized according to the Schechter function with 
$\phi^* / \textrm{Mpc}^{-3} =(1.8 \pm 0.5) \times 10 ^{-3}$, $M^*_{1500} = -20.04\pm 0.12$ 
and $\alpha = -1.71 \pm 0.11$.

@@

Finkelstein
HST using CANDELS/GOODS fields, HUDF and Hubble Frontier Field deep parallel observations near the Abell 2744 and MACS J0416.1-2403 clusters. (Unlensend fields)

>>>>

The data from the Hubble Space Telescope Legacy (HSTL) \citep{bouwens14} is a compilation 
of observations since the installation of the Advanced Camera for Surveys (ACS) in 2002, 
through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in 2009, up to 2012. 
The HST fields of view are: XDF, HUDF09-1, HUDF09-2, CANDELS-S/Deep, 
CANDELS-S/Wide, ERS, CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS, 
CANDELS-COSMOS and CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2, 
40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area corresponds 
to $\sim 0.7 \deg^2$ over five different lines of sight, reducing cosmic variance effects. 
Two cameras performed the observations: ACS and WFC3/IR, using 
$B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$, $J{125}$, 
$JH_{140}$ and $H_{160}$ filters.
The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in the 
deepest field (XDF). Total number of z=6 LBG candidates is 940, most of them in the faint 
end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
\citet{bowens14} calculated LF using a stepwise maximum-likelihood (SWML) based on \citet{efstathiou88}. 
The Schechter parameters derived are: 
$\phi^* / \textrm{Mpc}^{-3} =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}$, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
\citet{bouwens14} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.

\citet{finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS fields, along with two of the Hubble Frontier Fields (HFF): deep parallel observations (unlensed fields) near the Abell 2744 and MACS J0416.1-2403 clusters. The HFF uses the ACS and the WFC3/IR with the same filters aforementioned but $z_{850}$.

\citet{willott13} presented the sixth release of the Canada-France-Hawaii 
Telescope Legacy Survey CFHTLS. The observations where performed over four 
separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives this 
survey great robustness. Optical observations used MegaCam  %%%%%%[CITE REQUIRED] 
with $u^* g' r' i' z'$ filters. The main selection criteria: all the 
objects must be brighter than magnitude $z' = 25.3$. The final 
number of LBGs founded was 40. Moreover, they get spectroscopic confirmation 
for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which 
has a $\ll 5.5$-square arcmin field of view . They show incompleteness in the sample due to 
foreground contamination and the detection algorithm; there is no warranty to 
have every object brighter than the limit magnitude on the faint limit. The full 
galaxy LF at $z=6$ cannot be obtained as in other studies. Nevertheless, this survey 
was focussed on the highly luminous LBGs. LF is calculated using the stepwise 
maximum likelihood method of \citet{efstathiou88}, within 
magnitudes 
from $M_{1350} = -22.5$ up to $-20.5$. The luminosity function of $z=5.9$ shows 
an exponential decline at the bright end, where feedback processes and inefficient 
last cooling limites star forming in bright galaxies hosted in the most massive halos.

\citet{mclure09} build the luminosity function for $z=5$ and $z=6$ using data from two ground-based
 telescopes: the United Kingdom Infrared Telescope in the near-IR imaging and Subaru 
 Telescope for the optical imaging. They use the first data release of the UKIRT Infrared 
 DeepSky Survey Ultra Deep Survey (UDS), together with the Subaru XMM-Newton 
 Survey (SXDS). Total observed area is $0.63 \deg^2$ uniformly covered by booth catalogues.
The UKIRT was equipped with the WFCAM using $J K$ filters. The Subaru was equipped 
with the Suprime-Cam with the $B V R i' z'$ filters. All candidates where brighter than 
$z'=26$. The UV rest frame magnitude range is $-22.4\leq M_{1500} \leq-20.6$. The LF 
was calculated using the maximum likelihood estimator of \citet{schmidt68}. 
Their analysis gave a total number of 104 LBG candidates in the redshift range 
$5.7\leq z \leq 6.3$. LF was parameterized according to the Schechter function with 
$\phi^* / \textrm{Mpc}^{-3} =(1.8 \pm 0.5) \times 10 ^{-3}$, $M^*_{1500} = -20.04\pm 0.12$ 
and $\alpha = -1.71 \pm 0.11$.

@@
